Reasoning about a Capability Machine with Local Capabilities

### 2017-06-14 popl-2018/paper.tex
Added reasonable compiler provides protection (no detailed explanation).

The final question that remains is: where should we store this activation
record? The attentive reader may already see that there is only one possibility:
since the activation record contains the old stack pointer, which is local, the
activation record can only be constructed in a part of memory where we have
write-local access, i.e.\ on the stack. Note that this means we will be placing
and executing instructions on the stack, i.e.\ it will not just contain code
pointers and data. This means that our calling convention should be combined
with protection against stack smashing attacks (i.e.\ buffer overflows on the
stack overwriting activation records' contents). Luckily, such protection is
easy to provide thanks to the capability machine's fine-grained memory
protection\dominique{explain this point better}.

@@

To prove Lemma~\ref{lem:correctness-f1}, it suffices to show that the start
configuration is safe (in the $\observations$ relation) for a world with a
permanent region that requires the assertion flag to be 0. By an anti-reduction
lemma, it suffices to show that the configuration is safe after some reduction
steps. We then use a general lemma for reasoning about
\texttt{\footnotesize{scall}}, by which it suffices to show that (1) the
configuration that \texttt{\footnotesize{scall}} will jump to is safe and (2)
that the configuration just after \texttt{\footnotesize{scall}} is done cleaning
up is safe. We use the Fundamental Theorem to reason about the unknown code, but
notice that the adversary capability is an enter capability, which the
Fundamental Theorem says nothing about.\dominique{why doesn't it?} \lau{The FTLR says nothing about enter capabilities, because an enter capability cannot directly be used as a program counter. The reason being that the computation would fail immediately and the condition in the observation relation would immediately be true (as it requires the computation to terminate and not fail). It would be trivial to show that the enter capability, data and other capabilities without execute permission is in the expression relation.}  Luckily the enter capability becomes
$\exec$ after the jump and then the Fundamental Theorem applies.

>>>>

The final question that remains is: where should we store this activation
record? The attentive reader may already see that there is only one possibility:
since the activation record contains the old stack pointer, which is local, the
activation record can only be constructed in a part of memory where we have
write-local access, i.e.\ on the stack. Note that this means we will be placing
and executing instructions on the stack, i.e.\ it will not just contain code
pointers and data. This means that our calling convention should be combined
with protection against stack smashing attacks (i.e.\ buffer overflows on the
stack overwriting activation records' contents). Luckily, such protection is
easy for a reasonable compiler to provide thanks to the capability machine's
fine-grained memory protection\dominique{explain this point better}.

@@

To prove Lemma~\ref{lem:correctness-f1}, it suffices to show that the start
configuration is safe (in the $\observations$ relation) for a world with a
permanent region that requires the assertion flag to be 0. By an anti-reduction
lemma, it suffices to show that the configuration is safe after some reduction
steps. We then use a general lemma for reasoning about
\texttt{\footnotesize{scall}}, by which it suffices to show that (1) the
configuration that \texttt{\footnotesize{scall}} will jump to is safe and (2)
that the configuration just after \texttt{\footnotesize{scall}} is done cleaning
up is safe. We use the Fundamental Theorem to reason about the unknown adversarial code, but
notice that the adversary capability is an enter capability, which the
Fundamental Theorem says nothing about.
\dominique{why doesn't it?}
\lau{The FTLR says nothing about enter capabilities, because an enter capability cannot directly be used as a program counter. The reason being that the computation would fail immediately and the condition in the observation relation would immediately be true (as it requires the computation to terminate and not fail). It would be trivial to show that the enter capability, data and other capabilities without execute permission is in the expression relation.}
Luckily the enter capability becomes
$\exec$ after the jump and then the Fundamental Theorem applies.
